 Casting multiple shadows: high-dimensional interactive data visualisation with tours and embeddings

### 2020-06-23 paper.Rmd
start drafting case study

(ref:fake-trees) Example high-dimensional tree shaped data, $n = 3000$ and $p = 100$. The data lies 2-d tree like structure consisting of ten branches. This data is available in the `phateR` package and is simulated via diffusion-limited aggregation (a random walk along the branches of the tree) with Gaussian noise added [@Moon2019-ce].

@@

This will be Macosko data

>>>>

(ref:fake-trees) Example high-dimensional tree shaped data, $n = 3000$ and $p = 100$. The data lies 2-d tree like structure consisting of ten branches. This data is available in the `phateR` package and is simulated via diffusion-limited aggregation (a random walk along the branches of the tree) with Gaussian noise added. [@Moon2019-ce].

@@

A common analysis task in single cell studies is performing clustering to
identify groupings  of cells with similar expression profiles. Analysts
in this area generally use non linear DR methods for verification and identifaction
of clusters and developmental trajectories (i.e., case study 1). For clustering,
workflows the primary task is verify the existence of clusters and then begin to 
identify the clusters as cell types using the expression of "known" 
marker genes. The task becomes harder if the goal is discovery of new cell
types

Here we describe a liminal view of mouse single cell data from @Macosko2015-ot
following the workflow described in @Amezquita2020-at. To begin we obtained
the count matrix from the `scRNAseq
